Circular Distributional Trees and Forests with an Application to Wind Direction Forecasting

### 2019-11-20 pkg/circtree/inst/wind_paper/draft/draft.Rnw
revision of Table 1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2889 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4cce6f566164abae43d4ae5bd11b83ab7d31a0f2

\begin{table}[t!]
%\resizebox{1.4\textwidth}{!}{
\begin{minipage}{\textwidth}
\caption[Table caption text]{Overview of the employed data set.}
\label{tab:data}
\begin{tabular}{l  l}
\hline
Data components              & Description \\
\hline
Meteorological variables     & Wind direction, wind speed, air pressure, \\
                             & temperature, relative humidity \\
Derived quantities           & 3-hourly means, minima, maxima; \\
                             & 1-hourly and 3-hourly temporal changes; \\
                             & spatial differences towards the airport\\
Weather stations (Innsbruck) & 21 stations at the airport, \\
                             & Landeck, Kufstein, Steinach, \dots \\
Weather stations (Vienna)    & 22 stations at the airport, \\
                             & \ldots \\
%\emph{dd}: wind direction       & different locations, \\
%                                & changes over time(?)\\
%\emph{ff}: wind speed           & different locations, \\
%                                & changes over time(?), \\
%                                & (hourly) maxima\\
%\emph{p}: pressure              & different locations, \\
%                                & differences between locations, \\
%                                & changes over time(?)\\
%\emph{t}: temperature           & different locations, \\
%                                & changes over time(?)\\
%\emph{rf}: relative humidity    & different locations\\
\hline
\end{tabular}
\end{minipage} 
%}
\end{table}

>>>>

\begin{table}[t!]
\caption[Table caption text]{Overview of the employed data sets for the case study. For Innsbruck and Vienna,
 various meteorological variables and derived quantities of these are considered at the respective stations, located directly  at the airports or in their vicinities.}
\label{tab:data}
\begin{center}
\begin{tabular}{l  l}
%\noalign{\vskip 1mm}                  
\hline
Data components               & Description \\
\hline
Meteorological variables:     & Wind direction, wind (gust) speed, \\
                              & (reduced) air pressure, relative humidity, \\
                              & temperature\\ 
\noalign{\vskip 1mm}                           
Derived quantities:           & 3-hourly means/minima/maxima, \\
                              & 1-hourly and 3-hourly temporal changes, \\
                              & spatial differences towards the airport\\
\noalign{\vskip 1mm}                              
Weather stations (Innsbruck): & 4 stations at the airport, \\
                              & Igls, Kematen, Kufstein, Landeck, Patscherkofel, \\
                              & Steinach\\
\noalign{\vskip 1mm}
Weather stations (Vienna):    & 9 stations at the airport, \\
                              & Arsenal, Donaufeld, Exelberg, G\"anserndorf, \\
                              & Gro{\ss}-Enzersdorf, Gumpoldskirchen, Hohe Warte,\\
                              & Innere Stadt, Jubil\"aumswarte, Mariabrunn, \\
                              & Seibersdorf, Unterlaa, Wolkersdorf\\
\hline
\end{tabular}
\end{center}
\end{table}
